

\bibitem{Oc1}
	Назаров, С. В. 
	Современные операционные системы: учебное пособие 
	/ С. В. Назаров, А. И. Широков. 
	— Москва : Национальный Открытый Университет «ИНТУИТ», 2012.

\bibitem{Oc2}
	Основные понятия ОС 
	[Электронный ресурс].
	 — Режим досту­па: http://technomag.bmstu.ru/doc/48639.html
	 — Дата доступа: 11.12.2017.

\bibitem{linuxOffDoc}
	Операционные системы Linux 
	[Электронный ресурс].
	 — Ре­жим доступа: http://help.ubuntu.ru/wiki/linux
	 — Дата доступа: 11.12.2017.
	 
\bibitem{linuxDistr}
	 Linux-2017: самые перспективные дистрибутивы  
	 [Электронный ресурс].
	 — Ре­жим доступа: https://habrahabr.ru/company/ruvds/blog/320002/
	 — Дата доступа: 11.12.2017.

\bibitem{2part-1}
	За пределами Стандартной модели
	[Электронный ресурс].
	 — Режим доступа: https://elementy.ru/LHC/HEP/SM/beyondSM 
	 — Да­та доступа: 11.12.2017.


\bibitem{Krasnikov:2004}
	Н. В. Красников, В. А. 
	Матвеев. Поиск новой физики на LHC
	[Электронный ресурс].
	 — Режим доступа: http://nuclphys.sinp.msu.ru/ATLAS\_exp/at03.htm 
	 — Дата доступа: 11.12.2017.
	 
\bibitem{2part-pythia-all}
	 Official documentation
	 [Электронный ресурс].
	 — Режим доступа: http://home.thep.lu.se/~torbjorn/Pythia.html 
	 — Дата доступа: 11.12.2017.
% Статья
\bibitem{Bobovnikov:2016}
	Бобовников, И.Д. Эффекты $Z-Z^\prime$-смешивания в процессах рождения пары $W^±$-бозонов на адронных и лептонных коллайдерах высоких энергий
	/ И.Д. Бобовников, А.А. Панков.
	— Письма в ЭЧАЯ, 2016. T. 13, №1(199). С.8-35
	
\bibitem{nuclphys:weak}
	Слабое взаимодействие 
	[Электронныйресурс].
	— Режим доступа: http://nuclphys.sinp.msu.ru/enc/e149.htm
	— Дата доступа: 11.12.2017.

% Book
	 
\bibitem{2part-pankov}
	Osland, P. Probing $Z-Z^\prime$ mixing with ATLAS and CMS resonant diboson production data at the LHC at $\sqrt{s}=13$ TeV
	/ P. Osland, A.A. Pankov, A.V. Tsytrinov 
	// Physical Review D. – 2012. – Vol. 86. – P. 12.
% 7
\bibitem{andreev-pankov:2012}
	Andreev, V. V. Constraints on the $Z-Z^\prime$ mmixing angle from data measured for the process $e^+e^- \rightarrow W^+W^-$ at the LEP2 collider
	/ V.V. Andreev, A.A. Pankov
	// Phys. At. Nucl. – 2012. – Vol. 75. – P. 76.
% 8	
\bibitem{schael:2006}
	ALEPH and DELPHI and L3 and OPAL and SLD Collaborations and LEP Electroweak Working Group and SLD Electroweak Group and SLD Heavy Flavour Group
	/ Schael, S. [et al.] 
	// Precision electroweak measurements on the Zresonance, Phys. Rep. 2006. – P. 427.
% 19
\bibitem{sirunyan:2017}
	Search for massive resonances decaying into $WW$, $WZ$ or $ZZ$ bosons in proton-proton collisions at $\sqrt{s}=13$ TeV
	/ Sirunyan, A. M. [et al.] 
	// J. High Energy Phys. – 2017. – Vol. 162. – P. 56.
% 26
\bibitem{ada-wwz:2013}
	Measurement of $W^+W^-$−production in pp collisions at $\sqrt{s}=7$ TeV with the ATLAS detector and limits on anomalous $WWZ$ and $WW_y$ couplings
	/ Ada, G. [et al.] 
	// Phys. Rev. D. – 2013. – Vol. 88. – P. 29.
% 25	
\bibitem{ada-lvlv:2013}
	Search for new phenomena in the $WW \rightarrow lvl^{\prime}v^{\prime}$ final state in $pp$ collisions at $\sqrt{s}=7$ TeV with the ATLAS detector
	/ Ada, G. [et al.] 
	// Physics Letters B. – 2013. – Vol. 3. – P. 878.
	




